CFRD Screening Survey

### 2023-04-10 Christine Chan/CFRD Screening Survey/cfrd_screening_analysis.Rmd
center type comparisons CFRD screening

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(broom)
library(gtsummary)
library(knitr)
knitr::opts_chunk$set(echo = FALSE,message = FALSE)
if(Sys.info()["sysname"] == "Windows"){
  home_dir = "S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Linux"){
  home_dir = "~/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Darwin"){
  home_dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
}
knitr::opts_knit$set(root.dir = home_dir)
rm(home_dir)
source("~/GitHub/CF/get_genotype_class_severity.R")
```

@@

# Hypothesis Tests

## Centers with at least 50% of patients with state-funded health insurance have less than50% OGTT completion rates (CF center directors survey, questions #4 and #6).

@@

>>>>

```{r setup, include=FALSE}
library(arsenal)
library(tidyverse)
library(performance)
library(broom)
library(gtsummary)
library(knitr)
knitr::opts_chunk$set(echo = FALSE,message = FALSE)
if(Sys.info()["sysname"] == "Windows"){
  home_dir = "S:/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Linux"){
  home_dir = "~/UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
} else if (Sys.info()["sysname"] == "Darwin"){
  home_dir = "/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF"
}
knitr::opts_knit$set(root.dir = home_dir)
rm(home_dir)
source("~/GitHub/CF/genotype_class_severity.R")
```

@@

# OGTT Completion Rate

## Centers with at least 50% of patients with state-funded health insurance have less than 50% OGTT completion rates (CF center directors survey, questions #4 and #6).

@@

# Center Age Group

```{r}
non_endo$age_group = 
  factor(non_endo$What.patient.group.does.your.CF.center.take.care.of.)
endo$age_group = 
  factor(endo$What.age.group.of.CF.patients.do.you.take.care.of...please.select.all.that.apply.)
levels(endo$age_group) = c("Pediatric","Both","Both","Both","Adult")
```

## CF center directors

```{r results='asis'}
t1 = tableby(age_group ~ state_funded+ogtt_completion + endocrinologist + protocol + role + location +reminders,
             data = non_endo,control = list(cat.test = "fe"))
summary(t1,pfootnote = T)
```
